\begin{rSection}{Publications}

\textbf{Conference Papers}
\begin{description}[font=\normalfont]
%{{{
\item[{[C7]}]{
    \textbf{Wei Li}, Jialu Xia, Yuzhe Ma, Jialu Li, Yibo Lin, Bei Yu, 
    ``Adaptive Layout Decomposition with Graph Embedding Neural Networks'', 
    ACM/IEEE Design Automation Conference (\textbf{DAC}), San Francisco, July 19-23, 2020.
}
\item[{[C6]}]{
    Husheng Zhou, \textbf{Wei Li}, Yuankun Zhu, Yuqun Zhang, Bei Yu, Lingming Zhang, Cong Liu, 
    ``DeepBillboard: Systematic Physical-World Testing of Autonomous Driving Systems'', ACM/IEEE International Conference on Software Engineering (\textbf{ICSE}), Seoul, May 23–29, 2020.
}
\item[{[C5]}]{
    Yuzhe Ma, Zhuolun He, \textbf{Wei Li}, Tinghuan Chen, Lu Zhang, Bei Yu, 
    ``Understanding Graphs in EDA: From Shallow to Deep Learning'', ACM International Symposium on Physical Design (\textbf{ISPD}), Taipei, Mar. 25–Apr. 01, 2020. \textbf{(Invited Paper)}
}
\item[{[C4]}]{
    Yuzhe Ma, Ran Chen, \textbf{Wei Li}, Fanhua Shang, Wenjian Yu, Minsik Cho, Bei Yu, 
    ``A Unified Approximation Framework for Deep Neural Networks'', The IEEE International Conference on Tools with Artificial Intelligence (\textbf{ICTAI}) 2019. \textcolor{red}{\textbf{(Best Student Paper Award)}}
}
\item[{[C3]}]{
    \textbf{Wei Li}, Yuzhe Ma, Qi Sun, Yibo Lin, Iris Hui-Ru Jiang, Bei Yu, David Z. Pan,
    ``OpenMPL: An Open Source Layout Decomposer'', IEEE International Conference on ASIC (\textbf{ASICON}), Chongqing, China, Oct. 29–Nov. 1, 2019. \textbf{(Invited Paper)}
}
\item[{[C2]}]{
    Xia Li, \textbf{Wei Li}, Yuqun Zhang, Yuqun Zhang, Lingming Zhang, 
    ``DeepFL: Integrating Multiple Fault Diagnosis Dimensions for Deep Fault Localization'',The ACM SIGSOFT International Symposium on Software Testing and Analysis 
      (\textbf{ISSTA}), 2019. \textcolor{red}{\textbf{(Distinguished Paper Award)}}
}
\item[{[C1]}]{
    Bentian Jiang, Xiaopeng Zhang, Ran Chen, Gengjie Chen, Peishan Tu, \textbf{Wei Li}, Evangeline F. Y. Young, Bei Yu, 
    ``FIT: Fill Insertion Considering Timing'', 
    ACM/IEEE Design Automation Conference (\textbf{DAC}), Las Vegas, NV, June 2-6, 2019.
}


\end{description}


\end{rSection}

